Notes: New gaugings in 3d from three-form

### 2023-06-15 Draft_3dH3.tex
Renewed discussion of zeta family.

Finally, the metric parametrising this moduli space is:
\begin{equation}
	\begin{aligned}
		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg]\,.
	\end{aligned}
\end{equation}

>>>>

Finally, the metric parametrising this moduli space is:
\begin{equation}
	\begin{aligned}
		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg]\,.
	\end{aligned}
\end{equation}
As previously, the deformation breaks the isometry group down to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries. Note that for
\begin{equation}
	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2}\,\quad\Omega=\ts{\Omega}=0,
\end{equation}
the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for
\begin{equation}
	\chi_{1}=\pm\chi_{2}=\frac{\zeta_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad \ts{\chi}_{1}=\mp\ts{\chi}_{2}=-\frac{\ts{\zeta}_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad e^{2\psi}=\frac{1}{(1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2})^{2}},
\end{equation}
with ${\cal N}=(4,0)$ (or $(0,4)$) and symmetry enhancement to ${\rm SO}(4)\times{\rm U}(1)^{2}$. There seems to be no other points with (super)-symmetry enhancement in the scalar manifold.
